---
title: "> 06 <br> > getting more"
subtitle: "`r emo::ji('money_bag')` out of GitHub <br> `r emo::ji('link')` [rstd.io/design-ds-class](https://rstd.io/design-ds-class)"
author: "dr. mine çetinkaya-rundel"
date: "28 jan 2020"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["../../xaringan-themer.css", "../../slides-style.css"]
    nature:
      highlightStyle: solarized-light
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>`
---

```{r child = "../../setup.Rmd"}
```

--

class: middle, inverse

# Issue templates

---

## Issues for feedback

- Using GitHub issues for feedback can be somewhat cumbersome.
- Issue templates can ease the pain...
- Issue templates live in the `".github/ISSUE_TEMPLATE"` folder
- It's up to you whether you want to include these with your starter repo or add them after the deadline
  - To add after deadline, use the `repo_add_file()` function

<br>

[DEMO]

---

.your-turn[
Add a new issue to your neighbour's HW 01 repo using the issue template.
]

```{r echo=FALSE}
countdown(minutes = 3)
```

---

class: middle, inverse

# Merge conflicts

---

## Merge conflicts

- When two collaborators make changes to a file and push the file to their repo, git merges these two files.
- If these two files have conflicting content on the same line, git will produce a **merge conflict**.

---

## Prep

First, I'll add a simple text file to your team repos that you can use for practicing with merge conflicts, using the `repo_add_file()` function.

<br>

```
# Merge conflicts

This is line 1 of text.
This is line 2 of text.
This is line 3 of text.
This is line 4 of text.
```

<br>

[DEMO]

---

.your-turn[
- Launch your Lab 03 project in RStudio Cloud and pull changes from GitHub. This should bring in the new file you got added.
  - Alternatively, start fresh by cloning again from your Lab 03 repo.
- Assign the numbers 1, 2, 3, (and 4 if there are 4 people in your team) to each of the team members.
]

---

## Let's cause a merge conflict!

- Take turns in completing the exercise, only one member at a time.
- All other members should get up and look over the shoulder of the member who is doing the exercise.

---

## Member 1

- Change the text `This is line 1 of text.` to something else, e.g. `I love R!`. 
- Commit and push.

`r emo::ji("stop_sign")` Wait for instructions before moving on to the next step.

---

## Member 2 

- Do not pull! 
- Change the text `This is line 1 of text.` to something else, e.g. `I love RStudio!`. 
- Commit and attempt to push, you should get an error. 
- Pull. 
- Take a look at the document with the merge conflict. Clear the merge conflict by choosing the correct/preferred change. 
- Commit, and push.  

`r emo::ji("stop_sign")` Wait for instructions before moving on to the next step.

---

## Member 3

- Change the text `This is line 2 of text.` to something else, e.g. `I love data science!`. 
- Commit and attempt to push. You should get an error. 
- Pull. 
- No merge conflicts should occur. Now push.  

`r emo::ji("stop_sign")` Wait for instructions before moving on to the next step.

---

## Member 4

- Change the text `This is line 2 of text.` to something else, e.g. `Is it lunch time yet?`. 
- Commit and attempt to push. You should get an error. 
- Pull. 
- Take a look at the document with the merge conflict. 
- Clear the merge conflict by choosing the correct/preferred change. 
- Commit, and push.  

`r emo::ji("stop_sign")` Wait for instructions before moving on to the next step. 

---

## All members

- Back to your seats.
- Pull, and observe the changes in your document.

---

## Tips for collaborating via GitHub

- Always pull first before you start working.
- Commit, and push, often to minimize merge conflicts and/or to make merge conflicts easier to resolve.
- If you find yourself in a situation that is difficult to resolve, ask questions asap, don't let it linger and get bigger.

---

.your-turn[
- Work with your neighbor to design a different merge conflict activity. 
- It can be totally different, or a modified version of the one we did.
]

```{r echo=FALSE}
countdown(minutes = 10)
```

---

class: middle, inverse

# Automated feedback

---

## GitHub Actions

- GitHub Actions makes it easy to automate all your software workflows, now with world-class CI/CD. 
- Kick off workflows with GitHub events like push, issue creation, or etc.
- See https://github.com/rundel/ghclass-actions for more on GitHub actions and using them with ghclass.

---

class: middle

In this next bit, we'll work with HW 01, your individual repos.

---

## Does my Rmd knit?

You can check if your students' work is reproducible (e.g. does the Rmd knit) using GitHub Actions triggered each time they push.

---

`check-rmd.yml`

.small[
```yaml
on: 
  push:
    branches:
    - master
    paths:
    - 'hw-01-airbnb-edi.Rmd'  
name: Check Repo
jobs:
  check-rmd:
    runs-on: ubuntu-latest
    container:
      image: rocker/tidyverse:latest
    steps:
    - name: Checkout
      uses: actions/checkout@master
    - name: Check Rmd Rendering
      run:  Rscript -e "rmarkdown::render('hw-01-airbnb-edi.Rmd')"
```
]

[DEMO]

---

.your-turn[
- Launch your HW 01 project in RStudio Cloud and pull changes.
- Make a change in `hw-01-airbnb-edi.Rmd`, ideally one that would prevent the Rmd from knitting, e.g. add some faulty code to a code chunk. Knit the Rmd, confirm that it doesn't actually knit, but errors out. Commit and push anyway.
- Go to your repo on GitHub and observe the build fail, and badge change.
- Then, fix the code, confirm that your Rmd knits, then commit and push, and observe the build succeed and badge change to green.
]

```{r echo=FALSE}
countdown(minutes = 10)
```

---

## How is my code style?

- You can also provide feedback on students' code style using GitHub Actions. 

- This time we'll schedule daily feedback: https://crontab.guru/.

- Checks rely on the [Tidyverse style guide](https://style.tidyverse.org/) using the [**styler**](https://github.com/r-lib/styler) package.

---

.your-turn[
- Launch your HW 01 project in RStudio Cloud and pull changes.
- Make a change in one of the code chunks in `hw-01-airbnb-edi.Rmd`, ideally one with wonky style. See below for inspiration. Commit and push your changes.
- Next, we'll observe how the styling check works.
]

```{r eval=FALSE}
x=4
x*3
(x+2)/   (  23+x  )
```

```{r echo=FALSE}
countdown(minutes = 3)
```

---

`style.yml`

.small[
```yaml
on:
  schedule:
    - cron:  '15 12 * * *'
name: Style Repo
jobs:
  style:
    runs-on: ubuntu-latest
    container:
      image: rundel/ghclass:latest
    steps:
    - name: Run styler on repo
      env: 
        GITHUB_PAT: ${{ secrets.GITHUB_TOKEN }}
      run: |
        git config --global user.name "${GITHUB_ACTOR}"
        git config --global user.email "noreply@github.com"
        Rscript -e "ghclass::repo_style(\"${GITHUB_REPOSITORY}\", tag_collaborators = FALSE, prompt = FALSE)"
```
]

[DEMO]

---

.discussion[
Discuss with your neihbors other checks you can envision using in your assignments. Don't worry about the technical details of actually implementing them, we're just looking for ideas for now.
]

```{r echo=FALSE}
countdown(minutes = 3)
```
