---
title: "Intro Data Science"
resource_files:
- www/Aslanbek Pelle.png
- www/Chike Kravitz.png
- www/Devan Alamanni.png
- www/Fabian Grant.png
- www/Hersilia Haakonsson.png
- www/Karaugh Vaughn.png
- www/Maui Thrussell.png
- www/Neemias Vemulakonda.png
- www/Shaniqua Santiago.png
- www/Silver Leroy.png
- www/Terry Gasper.png
- www/Vin Nardo.png
- www/Tivoli Adamo.png
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    theme: bootstrap
---

```{r setup}
library(flexdashboard)
library(tidyverse)
library(wordcloud)
library(tidytext)
```

Individual students
=======================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}
student_survey <- read_csv("Getting to know you (Responses) - Form Responses 1.csv")

names(student_survey) <- c(
  "timestamp",
  "id", 
  "name",
  "preferred_name",
  "pronounciation",
  "pronouns",
  "github_name",
  "unique",
  "know_other",
  "learn_best",
  "fav_class",
  "programming",
  "statistics",
  "songs",
  "learn_goal",
  "concern",
  "clarify",
  "read_slides",
  "hear_lecture",
  "photo"
)


student_survey <- student_survey %>%
  arrange(name)
```

```{r}
selectInput(inputId = "student",
            label = "Select a student",
            choices = student_survey$name)
```

```{r}
selected_student <- reactive({
  student_survey %>%
    filter(name == input$student)
})
```

```{r}
renderImage(
  {
    list(src = paste0("www/", input$student, ".png"),
         contentType = "image/png",
         width = 230)
  },
  deleteFile = FALSE
)
```

Row
-----------------------------------------------------------------------

### Preferred name {.value-box}

```{r}

renderValueBox({
  preferred_name <- selected_student() %>%
    select(preferred_name)
  
  valueBox(
    value = preferred_name,
    icon = "fa-portrait"
  )
})
```

### Pronounciation {.value-box}

```{r}
renderValueBox({
  pronounciation <- selected_student() %>%
    mutate(pronounciation = if_else(is.na(pronounciation), preferred_name, pronounciation)) %>%
    select(pronounciation)
  valueBox(
    value = pronounciation,
    icon = "fa-microphone",
    color = "success"
  )
})
```

### Pronouns {.value-box}

```{r}
renderValueBox({
  pronouns <- selected_student() %>%
    mutate(pronouns = if_else(is.na(pronouns), "", pronouns)) %>%
    select(pronouns)
  valueBox(
    value = pronouns,
    icon = "fa-user-check",
    color = "info"
  )
})
```

Row
-----------------------------------------------------------------------

### Hope to learn... {data-width=200}


```{r}
renderText(selected_student()$learn_goal)
```

### Programming language before? {data-width=200}

```{r}
renderText(selected_student()$programming)
```

### Statistics course before? {data-width=200}

```{r}
renderText(selected_student()$statistics)
```

Row
-----------------------------------------------------------------------

### Anything else you would like me to know about you? {data-width=500}

```{r}
renderText(selected_student()$know_other)
```

Row
-----------------------------------------------------------------------

### Something cool / unique about yourself {data-width=200}

```{r}
renderText(selected_student()$unique)
```

Row
-----------------------------------------------------------------------

### How do you learn best? {data-width=500}

```{r}
renderText(selected_student()$learn_best)
```

Row
-----------------------------------------------------------------------

### What, if anything, concerns you about this course? {data-width=500}

```{r}
renderText(selected_student()$concern)
```

Overall
=======================================================================

```{r}
student_survey_oa <- student_survey %>%
  mutate(
    read_slides = fct_other(read_slides, keep = c("Yes", "No")),
    read_slides = fct_relevel(read_slides, "Yes", "No", "Other"),
    hear_lecture = fct_other(hear_lecture, 
                             keep = c("Yes", "No", "No, heard the professor but not the questions / answers from students who participated")),
    hear_lecture = fct_recode(hear_lecture,
                              `Heard prof,\nbut not student questions` = "No, heard the professor but not the questions / answers from students who participated"),
    hear_lecture = fct_relevel(hear_lecture, "Yes", "No", "Heard prof,\nbut not student questions", "Other")
    ) %>%
  filter(
    !is.na(hear_lecture),
    !is.na(read_slides)
  )
```


Row
-----------------------------------------------------------------------

### Were you able to read the slides on the board easily during the first lecture? {data-width=200}

```{r fig.width = 10}
ggplot(student_survey_oa, aes(x = read_slides, fill = read_slides)) +
  geom_bar() +
  coord_flip() +
  scale_fill_viridis_d() +
  guides(fill = "none") +
  labs(x = "", y = "") +
  theme_minimal() +
  theme(text = element_text(size = 22))
```


### Were you able to hear everything well during the first lecture? {data-width=200}

```{r fig.width = 10}
ggplot(student_survey_oa, aes(x = hear_lecture, fill = hear_lecture)) +
  geom_bar() +
  coord_flip() +
  scale_fill_viridis_d() +
  guides(fill = "none") +
  labs(x = "", y = "") +
  theme_minimal() +
  theme(text = element_text(size = 22))
```

Row
-----------------------------------------------------------------------

### What, if anything, concerns you about this course? {data-width=200}

```{r}
pal <- brewer.pal(4, "Blues")
```

```{r}
student_survey_oa %>%
  select(concern) %>%
  unnest_tokens(word, concern) %>%
  anti_join(stop_words, by = c("word" = "word")) %>%
  filter(!(word %in% c("23rd", "concerns"))) %>%
  count(word) %>%
  with(wordcloud(word, n, random.order = FALSE, colors = pal))
```

### Is there anything you would like me to clarify about the course? {data-width=200}

```{r}
student_survey_oa %>%
  select(clarify) %>%
  unnest_tokens(word, clarify) %>%
  anti_join(stop_words, by = c("word" = "word")) %>%
  filter(word != "23rd") %>%
  count(word) %>%
  with(wordcloud(word, n, random.order = FALSE, colors = pal))
```


